\documentclass[]{mcdowellcv}
\usepackage{amsmath}
\usepackage{hyperref}
\name{Holt Skinner}
\address{
    Austin, TX
    \linebreak \href{mailto:skinnerholt@gmail.com}{skinnerholt@gmail.com}
    }
\contacts{
    \href{https://linkedin.com/in/holt/}{linkedin.com/in/holt}
    \linebreak \href{https://github.com/holtskinner/}{github.com/holtskinner}
    }

\begin{document}

    \makeheader
    
    \begin{cvsection}{Employment}
    
        \begin{cvsubsection}{Technical Solutions Engineer}{Google}{October 2019 -- Present}
            \begin{itemize}
            \item Performed customer troubleshooting and collaborated with engineering teams to repair issues in Cloud products.
            \item Worked with high-valued Enterprise Customers and Escalations.
            \item Mentored new hires and taught training sessions.
            \item Worked as the Product Supportability Lead for the Cloud Machine Learning products.
            \end{itemize}
        \end{cvsubsection}

        \begin{cvsubsection}{Cloud Technical Resident}{Google}{July 2018 -- October 2019}
            \begin{itemize}
            \item Rotated between the roles of Customer Engineer, Cloud Consultant, and Technical Solutions Engineer.
            \item Created the UI for a custom workflow management tool currently in use by all of Google Cloud Support.
            \item Influenced over \$50 million in Cloud Sales.
            \item Wrote code for and published the top viewed
            \href{https://cloud.google.com/blog/products/ai-machine-learning/building-a-document-understanding-pipeline-with-google-cloud}{Google Cloud Blog AI/ML post} of 2019.
            \end{itemize}
        \end{cvsubsection}

        \begin{cvsubsection}{Software Engineer, Intern}{Amazon}{May 2017 -- August 2017}
            \begin{itemize}
            \item Developed the user interface, database, and controller for the \href{https://play.google.com/store/apps/details?id=com.amazon.klite&hl=en}{Kindle Lite} Android application.
            \item Deployed to the Google Play Store in November 2017.
            \end{itemize}
        \end{cvsubsection}

        \begin{cvsubsection}{Software Engineer, Intern}{Cerner, Tiger Institute}{May 2016 -- May 2017}		
            \begin{itemize}
                \item Implemented a user interface to display the NEDOCS score for the University of Missouri Hospital.
                \item Created a data analytics application to track use cases and errors for client-facing applications.
            \end{itemize}
        \end{cvsubsection}

        \begin{cvsubsection}{Teaching Assistant}{University of Missouri}{August 2015 - May 2018}
            \begin{itemize}
                \item Designed curriculum and taught three semesters of a freshman seminar course in Computer Science.
                \item Taught introductory Algorithm Design course in C and created lab assignments for 300 students.
            \end{itemize}
        \end{cvsubsection}

    \end{cvsection}
    
    \begin{cvsection}{Education}
        \begin{cvsubsection}{GPA: 3.975}{University of Missouri}{August 2014 -- May 2018}
            \begin{itemize}
                \item \textbf{Computer Science, Bachelor of Science}, Minors: Mathematics \& Information Technology
                \item Advanced Algorithms; Operating Systems; Computational Intelligence; Machine Learning; Web Dev; Object-Oriented Design;
                        iOS Development; Software Engineering; Databases; Networks; Computer Organization
            \end{itemize}
        \end{cvsubsection}
    \end{cvsection}
    
    \begin{cvsection}{Technical Experience}
    
        \begin{cvsubsection}{Languages and Technologies}{}{}
            \begin{itemize}
                \item C, Python, Go, SQL, JavaScript/TypeScript, Java, HTML/CSS, Swift, PHP, Assembly
                \item Google Cloud, Git, React, Android, UNIX, Bootstrap, Vue, Node.js, Splunk, Agile, Scrum
            \end{itemize}
        \end{cvsubsection}

        \begin{cvsubsection}{Projects}{}{}
            \begin{itemize}
               \item \textbf{NFL Predictor} (2017-2018) Worked in a team to create an application for predicting the outcomes of NFL games using Fuzzy C-Means Clustering and a Neural Network. Python, Numpy, HTML/CSS, JavaScript
                \item \textbf{Multi-layer Perceptron} (2017) Implemented Multi-layer Perceptron Neural Network trained with back-propagation. Swift
                \item \textbf{Hack Mizzou/Tiger Hacks} (2016-2017) Director of annual hackathon at the University of Missouri. Over 300 competitors, volunteers, sponsors, and mentors attended. 50 teams demoed a project.
            \end{itemize}
        \end{cvsubsection}

    \end{cvsection}
    
    \begin{cvsection}{Certifications and Organizations}
        \begin{cvsubsection}{}{}{}	
            \begin{itemize}
                \item \href{https://www.credential.net/profile/holtskinner}{\textbf{Google Cloud Certifications:}} Cloud Engineer, Cloud Architect, Cloud Developer, Data Engineer, Security Engineer, Network Engineer, Collaboration Engineer, DevOps Engineer
                \item \textbf{Association of Computing Machinery:} (Fall 2014 -- Spring 2018) Hackathon Director
                \item \textbf{Upsilon Pi Epsilon:}  (Fall 2016 -- Spring 2018)
                \item \textbf{MU University Singers:} (Fall 2014 -- Spring 2018) Social Media Chair
            \end{itemize}
        \end{cvsubsection}
    \end{cvsection}
\end{document}
